%% This defines the bibliography file (main.bib) and the bibliography style.
%% If you want to create a bibliography file by hand, change the contents of
%% this file to a `thebibliography' environment.  For more information 
%% see section 4.3 of the LaTeX manual.
% \begin{singlespace}
% \bibliography{main}
% \bibliographystyle{plain}
% \end{singlespace}

\begin{thebibliography}{99}
\begin{singlespace}
\raggedright

\bibitem{dnc-hack}
``Top Democrat's emails hacked by Russia after aide made typo, investigation finds," December 14, 2016. Available: \url{https://www.theguardian.com/us-news/2016/dec/14/dnc-hillary-clinton-emails-hacked-russia-aide-typo-investigation-finds}

\bibitem{wannacry-uk}
``UK hospitals hit with massive ransomware attack," May 12, 2017. Available: \url{https://www.theverge.com/2017/5/12/15630354/nhs-hospitals-ransomware-hack-wannacry-bitcoin/}

\bibitem{phishme-report}
``2016 Enterprise Phishing Susceptibility and Resiliency Report," 2016. Available: \url{https://phishme.com/2016-enterprise-phishing-susceptibility-report/}

\bibitem{91phishing}
``91\% Of Cyberattacks Start With A Phishing Email," December 13, 2016. Available: \url{http://www.darkreading.com/endpoint/91–of-cyberattacks-start-with-aphishing-email/d/d-id/1327704}

\bibitem{phishing-example-paypal}
``Phishing Example: PayPal - We need your help," March 22, 2016. Available: \url{https://security.berkeley.edu/news/phishing-example-paypal-we-need-your-help}

\bibitem{phishing-example-malware}
``Phishing Example: Messages containing Locky malware," August 24, 2016. Available: 
\url{https://security.berkeley.edu/news/phishing-example-messages-containing-locky-malware}

\bibitem{deep-packet-inspection}
``Firewall Evolution - Deep Packet Inspection," July 28, 2003. Available: \url{https://www.symantec.com/connect/articles/firewall-evolution-deep-packet-inspection}

\bibitem{qubes-os}
``Qubes OS: A resonably secure operating system." Available: \url{https://www.qubes-os.org/}

\bibitem{xen}
``The Xen Project, the powerful open source industry standard for virtualization." Available: \url{https://www.xenproject.org/}

\bibitem{bromium}
``Understanding Bromium\textsuperscript{\textregistered} Micro-virtualization for Security Architects." Available:
\url{https://www.bromium.com/sites/default/files/Bromium\%20Microvirtualization\%20for\%20the\%20Security\%20Architect_0.pdf}

\bibitem{marketsharereport}
``Google's Chrome Browser crushes the desktop competition in 2016," Feb 16, 2017. Available: \url{https://www.forbes.com/sites/kevinmurnane/2017/02/16/googles-chrome-browser-crushes-the-desktop-competition-in-2016/}

\bibitem{chromesandbox}
``Sandbox." Available: \url{https://chromium.googlesource.com/chromium/src/+/master/docs/design/sandbox.md}

\bibitem{google-docs-phishing}
``Google Docs users hit with sophisticated phishing attack," May 3, 2017. Available: \url{https://www.theverge.com/2017/5/3/15534768/google-docs-phishing-attack-share-this-document-with-you-spam}

\bibitem{gmail-spam-filter-list}
``Why emails are automatically marked as spam." Available: \url{https://support.google.com/mail/answer/1366858#warnings}

\bibitem{eros}
``Design of the EROS Trusted Window System." Available: \url{https://www.usenix.org/legacy/publications/library/proceedings/sec04/tech/full_papers/shapiro/shapiro.pdf}

\bibitem{fake-attachment-scam}
``Beware This Clever `Fake Attachment' Gmail Phishing Scam," Mar 15, 2017.Available: \url{https://www.lifehacker.com.au/2017/03/beware-this-clever-fake-attachment-gmail-phishing-scam/}

\bibitem{malvertising}
``What is Malvertising?" September 5, 2014. Available: \url{https://www.kaspersky.com/blog/what-is-malvertising/5928/}

\bibitem{malvertisement-nytimes}
``New York Times, BBC and others inadvertently serve up dangerous ads," March 16, 2016. Available: \url{https://www.cnet.com/news/new-york-times-bbc-dangerous-ads-ransomware-malvertising/}


\bibitem{punycode-attack}
``Chrome, Firefox and Opera vulnerable to Punycode phishing attack," April 20, 2017. Available: \url{https://www.theinquirer.net/inquirer/news/3008708/chrome-firefox-and-opera-vulnerable-to-punycode-phishing-attack}

\bibitem{chinese-ca}
``Chinese Certificate Authority `mistakenly' gave out SSL Certs for GitHub Domains,'' August 29, 2016. Available: \url{http://thehackernews.com/2016/08/github-ssl-certificate.html}

\bibitem{rfc-referrer}
``RFC 7231 - Hypertext Transfer Protocol (HTTP/1.1) - Section 5.5.2," June 2014. \url{https://tools.ietf.org/html/rfc7231#section-5.5.2}

\bibitem{mozdev-referrer}
``Referrer." \url{https://developer.mozilla.org/en-US/docs/Web/HTTP/Headers/Referer}

\bibitem{subresource-integrity}
``Subresource Integrity," June 23, 2016. Available: \url{https://www.w3.org/TR/SRI/}

\bibitem{subresource-integrity-2}
``Subresource Integrity." Available:  \url{https://developer.mozilla.org/en-US/docs/Web/Security/Subresource\_Integrity}

\bibitem{attack-verify-email}
``Beware of ``Email Deactivation - Verify Your Email Address" Microsoft Phishing Scam," June 7, 2016. Available: \url{https://www.onlinethreatalerts.com/article/2016/6/7/beware-of-email-deactivation-verify-your-email-address-microsoft-phishing-scam/}
\bibitem{attack-verify-email-1}
```Verify Your Email Account', The Latest Phishing Scam to Emerge Online," April 4, 2015. Available: \url{https://www.hackread.com/verify-your-email-account-the-latest-phishing-scam-to-emerge-online/}
\bibitem{attack-verify-email-2}
```Google email verification' message." Available: \url{https://support.google.com/accounts/answer/32044}
\bibitem{attack-verify-email-3}
``UChicago: Latest Email Scams." Available: \url{https://itservices.uchicago.edu/page/latest-email-scams}

\end{singlespace}
\end{thebibliography}